Cognate beginnings to bilingual lexical acquisition

### 2023-09-21 manuscript/manuscript.qmd

post_draws_list <- model_summary |>
    mutate(across(
        .value:.upper,
        \(x) ifelse(grepl("Intercept", .type),
            plogis(x), x / 4
        )
    )) |>
    split(model_summary$.variable)

re_data <- model_summary_re |>
    filter(.variable %in% c(
        "b_lv_std",
        "b_exposure_std:lv_std"
    ))

re_data_prop <- re_data |>
    mutate(
        is_positive = .value > 0,
        is_negative = .value < 0
    ) |>
    summarise(across(matches("is_"), mean),
        .by = .variable_name
    ) |>
    mutate(prop = ifelse(is_positive > is_negative,
        is_positive,
        is_negative
    ))
```

>>>>

post_draws_list <- model_summary |>
    mutate(across(
        .value:.upper,
        \(x) ifelse(grepl("Intercept", .type),
            plogis(x), x / 4
        )
    )) |>
    split(model_summary$.variable)
```
